\documentclass[11pt,a4paper,calibri]{moderncv}      
% \usepackage[english]{babel}



\moderncvstyle{classic}
\moderncvcolor{blue}                            

% character encoding
\usepackage[utf8]{inputenc}                     

% adjust the page margins
\usepackage[scale=0.75]{geometry}

% personal data
\name{Javad}{Ebrahimian Amiri}


\phone[mobile]{0468764362}               
\email{javad.amiri@anu.edu.au}                             


\begin{document}

\recipient{To}{
    Adaptive Optics Group Lead, \\*
    Research School of Astronomy and Astrophysics, \\*
    ANU College of Science
}

\date{\today}

\opening{
    I'm writing this statement to apply for the job number 528037, titled "\textit{Adaptive Optics Real-Time Software Engineer}", advertized on the ANU jobs website.
    I found this position aligned to my interests, experiences and capabilities.
}

\closing{Regards,}

\makelettertitle


% The first paragraph of your job application letter should include information on why you are writing. Mention the job you are applying for and where you found the position. If you have a contact at the company, mention the person's name and your connection here.

Here I address how I meet the selection criteria:
\vspace{0.2cm}
    \begin{enumerate}
        \item I hold a M.S. in software engineering from the University of Tehran, the most well-known university in Iran.
        I'm also in the final year of my Ph.D. in computer science at ANU.
        My research in both degrees has been focused on real-time systems.
        \item Both my M.S. and Ph.D. theses include design, implementation and testing of real-world software systems (e.g. RTOS and language VM).
        \item I have done large-scale software development using C/C++ or Rust as the core language. I have also been using Python as a scripting language and a test target for my Ph.D. thesis. As HPC experience, I have done a few postgraduate courses and research, on a wide range of topics including designing multi/many-core processors and co-processors, programming parallel architectures such as GPUs and Intel SIMD intructions, and multi-threaded paradigms like pthreads and openmp.
        \item I have done software development at operating-system and language runtime level, which requires permanent attention to multi-threading in various system aspects including design, implementation and performance evalation.
        \item My experience in developing realtime software includes addressing many technical (e.g. memory and device driver) and management (e.g. dividing responsibilities and documentation) challenges.
        \item In our research group at ANU, I am working as a team member responsible for design and implementation of a realtime variant of a software system. Software engineering practices such as agile Scrum are used in our group. It also includes solving many engineering problems.
        \item High-quality documentation has always been critical to my work, as it facilitates understanding other team members' works and clarifying my work to them.
        \item I appreciate the principles and policies towards equal opportunity, and I believe it is beneficial for indivuals, employers and the society.
    \end{enumerate}

% The next section of your cover letter should describe what you have to offer the company. Make strong connections between your abilities and the requirements listed in the job posting. Mention specifically how your skills and experience match the job. Expand on the information in your resume, don't just repeat it.

% Try to support each statement you make with a piece of evidence. Use several shorter paragraphs or bullets rather than one large block of text, which can be difficult to read and absorb quickly.

% Conclude your application letter by thanking the employer for considering you for the position. Include information on how you will follow-up. State that you will do so and indicate when (one week's time is typical). You may want to reduce the time between sending out your resume and follow up if you fax or email it.

I look forward to hearing from you.

\vspace{0.5cm}


\makeletterclosing

\end{document}